---
title: "Crypto Dynamic Presentation"
author: Try pressing "w" on your keyboard and press "o" for an overview of the slides.<br/> Use the arrows to navigate between slides and press "f" to fullscreen. <br/> [full version](https://cryptocurrencyresearch.org/).
date: '`r paste("Last Updated:<br/>",Sys.time(),"- UTC")`'
output: 
  ioslides_presentation: 
    self_contained: yes
    css: styles.css
runtime: shiny
---

```{r cache_all, include=FALSE}
# Once I'm done making edits get rid of the cache by commenting out the line below
#knitr::opts_chunk$set(cache = TRUE)
# automatically format all the code chunks
knitr::opts_chunk$set(tidy = TRUE)
# THIS IS SIMPLER + PRESENTATION VERSION
```

# Introduction

## Welcome to the more high-level version of the [predictive analytics example of how one could make trades on the cryptocurrency markets](https://cryptocurrencyresearch.org/).

You can navigate between topics with the right and left arrow keys, and press on the down key to learn more about each topic.

You can also press on the "o" key on your keyboard for an overview of the slides.

Press on the down arrow key on your keyboard to learn more about the differences between this version and the [full one](https://cryptocurrencyresearch.org/).

##
This version of the coded example also updates once a day at ~11:00AM UTC with the latest cryptocurrency data and predictive models, but the focus is around giving you as much boilerplate code that can be applied to a variety of other predictive analytics problems. The [full version](https://cryptocurrencyresearch.org/) deals with issues relating specifically to the cryptocurrency markets, and these will be avoided as much as possible in this version of the example.

<!-- You can navigate between topics with the right and left arrow keys, and press on the down key to learn more about each topic. -->

Press on the right arrow key on your keyboard to get started.

## Disclaimer

Enter disclaimer here


## Select Cryptocurrency

First, choose which cryptocurrency to analyze for the rest of this presentation. The rest of the slides will change accordingly.

```{r pull_data_hidden, include=F, cache=T}
# hide and pull data first in order to keep things in most logical order
library(PredictCrypto)
messari <- get_crypto_data()
# Adjust column names
messari <- janitor::clean_names(messari)
```


```{r crypto_selection, echo=F}
library(shiny)
inputPanel(
  selectInput("select_crypto", "Select a Cryptocurrency:", choices = unique(messari$name), multiple=F, selectize=TRUE, selected = "Ethereum")
)
```

```{r show_messari, echo=F, message=FALSE, warning=FALSE}
library(DT)
renderDT({
  datatable(head(subset(messari, name == input$select_crypto), 500),  style = "default", 
          options = list(scrollX = TRUE, pageLength=2, lengthMenu = c(2, 3, 5)), rownames = F)
})
```



## Visualize over time

```{r var_to_visualize, echo=F}
library(shiny)
inputPanel(
  selectInput("select_variable", "Variable to visualize:", choices = colnames(messari), multiple=F, selectize=TRUE, selected = "price_usd")
)
```


```{r visualize_over_time, echo=F, message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(anytime)
library(rlang)

# wrap with reactive environment
renderPlot({ 
  #Make necessary adjustments here and hide them (or give cleaned up data source):
  # Filter data:
  new_data <- subset(messari, name == input$select_crypto)
  # Convert date + date/time
  new_data$date_extracted <- anytime::anytime(new_data$date_extracted)
  new_data$date_time_colorado_mst <- anytime::anytime(new_data$date_time_colorado_mst)
  # Now plot the data:
  ggplot(new_data, aes_string(x="date_extracted", y=input$select_variable)) +
    geom_line() +
    ggtitle(paste0(input$select_crypto, ' - ', input$select_variable, ' over time'), 
            subtitle = paste0('Through: ', max(new_data$date_time_colorado_mst), ' - Colorado Time'))
})

```



In the [full version](https://cryptocurrencyresearch.org/) many assets are modeled at once which adds a layer of complexity to things.







<!-- ## Predictive Modeling -->

<!-- ```{r model_to_use, echo=F} -->
<!-- library(parsnip) -->
<!-- inputPanel( -->
<!--   selectInput("select_model", "Predictive Model:", choices = c('linear','XGBoost'), multiple=F, selectize=TRUE, selected = "linear") -->
<!-- ) -->
<!-- ``` -->

<!-- Also add adjustment for # of hours offset for target -->

<!-- ```{r predictive_modeling, echo=F, message=FALSE, warning=FALSE} -->
<!-- # wrap with reactive environment -->
<!-- renderTable({  -->
<!--   #Make necessary adjustments here and hide them (or give cleaned up data source): -->
<!--   # Filter data: -->
<!--   new_data <- subset(messari, name == input$select_crypto) -->
<!--   # Convert date + date/time -->
<!--   new_data$date_extracted <- anytime::anytime(new_data$date_extracted) -->
<!--   new_data$date_time_colorado_mst <- anytime::anytime(new_data$date_time_colorado_mst) -->

<!--   # Prices by exchange -->
<!--   exchange_prices <- get_prices_by_exchange() -->
<!--   new_data <- crypto_data_join(new_data, subset(exchange_prices, Exchange == 'HitBTC'))  -->
<!--   # Add target variable -->
<!--   new_data <- calculate_percent_change_daily_version(new_data, 24, 'hours') -->


<!--   # Train/Test split -->
<!--   #new_data <- cross_validate_crypto_5_more_data(new_data) -->

<!--   #new_data -->

<!-- }) -->
<!-- ``` -->







<!-- ## TO-DO: -->

<!-- - Data prep section -->

<!-- - User selection for what type of model to make -->

<!-- - New data source with prices filled in by exchange to avoid having to explain -->

















